\Huge Visualization Interactivity Perception Research \\ on Data Journalism

### 2017-05-01 paper/main.tex

For Question 1-4, time spends for Level 1 is less than Level 0, while time spends for Level 3 is more than the other two. So we can conclude that Some interactivity could help users to recognize the data faster. However, if the interactivity is too complex, users might have trouble to use the interaction. Therefore, designers must measure the complexity of their interactivity. The accuracy rate is random, so we can conclude that unsuitable designed interactivity can cause a misleading effect. However, since the Level 0 shows a significant higher skip rate in Question 1-4, we can conclude that the rich interactivity would make users engage more in the test. The low skip rate of Level 1 and Level 2 indicates that a rich interactivity would make users more willing to participate in the test and feel more confident on the test.
For question 5, surprisingly, the higher interactive level doesn't help users to get higher correctness. This may because the points in the scatter plot are clearly separated,  users could make a judgment by naked eyes. So the information obtained from the interactive doesn't help in this case. For question 6, the improvement of correctness from interactive is prominent. The higher interactive can help users to find the approximate average Trump vote, and decrease the influence of context misleading. On the other hand, the relatively high skip rate 
In this problem, if users are misleading by the context, they will tend to choose "Yes" over the correct answer "No." To further demonstrate the reduce of misleading, we compare the rate of "Misleading Answer" and "Right Answer" as shown in Fig. 5.

@@

We took a step out to evaluate if the different level of interactive can affect the audience of the newspapers online in data journalism. For the experiment itself, we used five kinds of the common interactive methods in the experiment, as the front-end technology fast changing, the future research should consider not only the classic methods but the latest visualization technology. Meanwhile, with the time limit, we can not find a more random sample to join this experiment, it should be improved in the future work.

@@

In the time spending part, we can see the significant higher time spending for high interaction, which might cause by the complexity. In the next stage, we can add a new group of participants that was introduced how to use these visualizations first. Measure the time spending, and accuracy/skip rate of this group might bring more insights. What's more, a more careful design of interaction need to be considered since the accuracy rate of Level 2, and Level 1 didn't outperform Level 1, which might be caused by lacking the learning stage for interaction.

>>>>

For Question 1-4, time spends for Level 1 is less than Level 0, while time spends for Level 3 is more than the other two. So we can conclude that Some interactivity could help users to recognize the data faster. However, if the interactivity is too complex, users might have trouble to use the interaction. Therefore, designers must measure the complexity of their interactivity. The accuracy rate is random, so we can conclude that unsuitable designed interactivity can cause a misleading effect. However, since the Level 0 shows a significant higher skip rate in Question 1-4, we can conclude that the rich interactivity would make users engage more in the test. The low skip rate of Level 1 and Level 2 indicates that a rich interactivity would make users more willing to participate in the test and feel more confident on the test.
For question 5, surprisingly, the higher interactive level doesn't help users to get higher correctness. This may because the points in the scatter plot are clearly separated,  users could make a judgment by naked eyes. So the information obtained from the interactive doesn't help in this case. For question 6, the improvement of correctness from interactive is prominent. The higher interactive can help users to find the approximate average Trump vote, and decrease the influence of context misleading. On the other hand, the relatively high skip rate may result from the less passionate of reading. In order to answer this question, users have to read the context throughtly, which may decrease users willing in answering. In this problem, if users are misleading by the context, they will tend to choose "Yes" over the correct answer "No." To further demonstrate the reduce of misleading, we compare the rate of "Misleading Answer" and "Right Answer" as shown in Fig. 5.

@@

We took a step out to evaluate if the different level of interactive can affect the audience of the newspapers online in data journalism. For the experiment itself, we used five kinds of the common interactive methods, as the front-end technology fast changing, the future research should consider not only the classic methods but the latest visualization technology. Meanwhile, with the time limitation, we can not find a more random sample to join this experiment, it should be improved in the future work.

@@

In the time spending part, the significant higher time spending for high interaction, which might cause by the complexity. In the next stage, we can add a new group of participants that was introduced how to use these visualizations first. Measure the time spending, and accuracy/skip rate of this group might bring more insights. What's more, a more careful design of interaction need to be considered since the accuracy rate of Level 2, and Level 1 didn't outperform Level 1, which might be caused by lacking the learning stage for interaction.
